Board Game Recommendation

### 2015-02-19 paper.Rnw
added reference files
quotes and urls

\documentclass[twoside]{article}
\usepackage{multicol}
\usepackage[hmarginratio=1:1, top=32mm, columnsep=20pt]{geometry}
\usepackage{amsmath}

@@

Board gaming, while being very popular among children, is a niche hobby beyond adolescence. Everyone may have grown up with Monopoly, but most people may have never heard of Citadels or Twilight Imperium. And as such, board gaming is a very difficult hobby to break into. "Gateway Games" such as Settlers of Catan or Ticket to Ride offer a gradual transition between the ultra-popular and mechanics-lite games like monopoly, to more rules-heavy games like Puerto Rico. The most difficult part of the transition, for most people, is actually finding new games to play. New games are often expensive for people who may be apprehensive about trying new games (a copy of Settlers of Catan goes for \$37.80 on Amazon.com). For this reason, a method to recommend games to people would be invaluable.

A few methods already exist, however, their usefulness varies. Boardgamegeek.com, a popular site among frequent board gamers, has a recommendation system that allows users to find a particular game they like, and then from there it will recommend more games that a person may like. A pretty thorough analysis of it and its issues can be found at http://boardgamegeek.com/wiki/page/Game\_Recommendation\_Algorithm. The bigget issue is that it cannot be tailored to an individual. You, an individual user, may have different preferences than the users as a whole, and it might be more useful to tailor recommendations to the individual.

A redditor identified this issue, and created a board game recoomender on the subreddit boardgamerecommender. You can "summon" the recommender by posting your boardgamegeek username anywhere on reddit, preceded by "/u/boardgamerecommender". This will prompt the bot to go search through your ratings of games on boardgamegeek, and then it will make a post with 4 lists of games: New games you may enjoy, older games you may enjoy, games you may find underrated, and games you may find overrated. This is a huge step forward for individuals that are looking for games, as they can now rate games they've played, and can then get recommendations for games they might like. However, there are a few drawbacks. The process has a few possible user inputs (such as playtime, number of players, category, mechanic, etc) that will narrow down the games that will be returned to the user. However, with each specification, a new recommendation will be generated, a process that is said to take 10-30 minutes (FIND A BETTER ESTIMATE FOR THIS). Also, there is no published methodology, so we cannot view how these recommendations are made.

@@

%\end{multicols}

>>>>

\documentclass[twoside]{article}
\usepackage{multicol}
\usepackage[hmarginratio=1:1, top=32mm, columnsep=20pt]{geometry}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{url}

\newcommand{\hh}[1]{{\color{magenta} #1}}

@@

Board gaming, while being very popular among children, is a niche hobby beyond adolescence. Everyone may have grown up with Monopoly, but most people may have never heard of Citadels or Twilight Imperium. And as such, board gaming is a very difficult hobby to break into. ``Gateway Games" such as Settlers of Catan or Ticket to Ride offer a gradual transition between the ultra-popular and mechanics-lite games like monopoly, to more rules-heavy games like Puerto Rico. The most difficult part of the transition, for most people, is actually finding new games to play. New games are often expensive for people who may be apprehensive about trying new games (a copy of Settlers of Catan goes for \$37.80 on Amazon.com). For this reason, a method to recommend games to people would be invaluable.

A few methods already exist, however, their usefulness varies. Boardgamegeek.com, a popular site among frequent board gamers, has a recommendation system that allows users to find a particular game they like, and then from there it will recommend more games that a person may like. A pretty thorough analysis of it and its issues can be found at \url{http://boardgamegeek.com/wiki/page/Game_Recommendation_Algorithm}. The bigget issue is that it cannot be tailored to an individual. You, an individual user, may have different preferences than the users as a whole, and it might be more useful to tailor recommendations to the individual.

A redditor identified this issue, and created a board game recoomender on the subreddit boardgamerecommender. You can ``summon" the recommender by posting your boardgamegeek username anywhere on reddit, preceded by ``/u/boardgamerecommender". This will prompt the bot to go search through your ratings of games on boardgamegeek, and then it will make a post with 4 lists of games: New games you may enjoy, older games you may enjoy, games you may find underrated, and games you may find overrated. This is a huge step forward for individuals that are looking for games, as they can now rate games they've played, and can then get recommendations for games they might like. However, there are a few drawbacks. The process has a few possible user inputs (such as playtime, number of players, category, mechanic, etc) that will narrow down the games that will be returned to the user. However, with each specification, a new recommendation will be generated, a process that is said to take 10-30 minutes (FIND A BETTER ESTIMATE FOR THIS). Also, there is no published methodology, so we cannot view how these recommendations are made.

@@

%\end{multicols}
\bibliographystyle{asa}
\bibliography{references}
